---
title: "linear model from Web"
author: "Gema Garcia"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot



```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS and ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```






### Numerical results




```{r}
cor(ARM~SIMS,data=data)
```



This shows there is a fair amount of relationship between SIMS and ARM in their strength. Which is 0.6860073.





### Inferential  (Build model.1)


```{r}
model.1 <- lm(ARM~SIMS,data=data)
summary.lm(model.1)
```



The residual standard error is 15.41 and our adjusted R squared is 0.467. We always look at the adjusted r squared when comparing. As you put more data, the r squared goes up.




#### Predict at target point


```{r}
mydata <-data.frame(GRIP=88, ARM=104)
```



did not let me predict and I do not know why





#### scatterplot with model fit




```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN

```



  

## Model 2 SIM~GRIP

### Now add in scatterplot



```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  labs(title = "SIMS and GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```







### Numerical results 



```{r}
cor(SIMS~GRIP,data=data)
```


The numerical result for SIMS~GRIP is 0.6398458.SIMS~ARM has a higher correlation than SIMS~GRIP.



### Inferential  (Build model.2)


```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```



The residual standard error is 1.295. SIMS~ARM is better than SIMS~GRIP because they have a better adjusted r squared.


  

#### predict model.2 at target point


```{r}
predict.lm(model.2, mydata, interval = "prediction")
```


The interval goes from 3.38 to positive 1.766.




#### now add the model fit to our plot for model.2




```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip

```
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)


```{r}
cor(SIMS~ARM+GRIP,data=data)
```


The correlation is larger than SIMS~ARM and SIMS~GRIP.



  
### Inferential  (Build 2-dimentional model.3)



```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```



This model has a standard residual error of 1.444 and a r squared of 0.5358.This model has a better residual error than SIMS~GRIP and SIMS~ARM.Model is SIMS= .0311 * ARM + .024470 * GRIP - 5.433871.




#### predict model.3 at target point


```{r}
predict.lm(model.3, mydata, interval = "prediction")
```


The interval goes from a negativee 1.716 to a positive 2.915.
  
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3



```{r}
anova(model.1, model.3)
```


Gives p value of 00000499, which does not have any value.We got a residual sum of squares from model 1. Such as 145, 34441, and 237.5.








### Model.2 vs Model.3

## Informally compare Model.1 with model.2

